Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-14 paper/structureScene.tex
remove dialog between ja and me on xi_1 and xi_2

We define second-order wavelets $\boldsymbol{\psi_{\gamma_2}}(t)$ in the same way as the first-order wavelets, but with parameters $\xi_2$, $J_2$, and $Q_2$ and so have center frequencies $2^{-\gamma_2/Q_2}\xi_2$ for $\gamma_2$ taking values between $0$ and $(J_2 \times Q_2 - 1)$. While this abuses notation slightly, the identity of the wavelets should be clear from context.
The amplitude modulation spectrum resulting from a wavelet modulus decomposition using these second-order wavelets is then
\begin{equation}
\boldsymbol{x_2}(t,\gamma_1,\gamma_2) =
\vert \boldsymbol{x_1} \ast \boldsymbol{\psi_{\gamma_2}} \vert(t,\gamma_1).
\end{equation}
In the sequel, we set $\xi_2$ to $2.5\,\mathrm{kHz}$, $Q_2$ to $1$, and $J_2$ to $12$. \ja{Why is $\xi_2 \neq \xi_1$?} \vl{$\xi_2 = \xi_1 / 8$ because $Q_1=8$}Lastly, the low-pass filter $\phi(t)$ is applied to $\boldsymbol{x_2}$ to guarantee local invariance to time-shifting, which yields
\begin{equation}
\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2) =
(\boldsymbol{x_2}(\cdot,\gamma_1,\gamma_2) \ast \phi)(t).
\end{equation}

>>>>

We define second-order wavelets $\boldsymbol{\psi_{\gamma_2}}(t)$ in the same way as the first-order wavelets, but with parameters $\xi_2$, $J_2$, and $Q_2$ and so have center frequencies $2^{-\gamma_2/Q_2}\xi_2$ for $\gamma_2$ taking values between $0$ and $(J_2 \times Q_2 - 1)$. While this abuses notation slightly, the identity of the wavelets should be clear from context.
The amplitude modulation spectrum resulting from a wavelet modulus decomposition using these second-order wavelets is then
\begin{equation}
\boldsymbol{x_2}(t,\gamma_1,\gamma_2) =
\vert \boldsymbol{x_1} \ast \boldsymbol{\psi_{\gamma_2}} \vert(t,\gamma_1).
\end{equation}
In the sequel, we set $\xi_2$ to $2.5\,\mathrm{kHz}$, $Q_2$ to $1$, and $J_2$ to $12$. Lastly, the low-pass filter $\phi(t)$ is applied to $\boldsymbol{x_2}$ to guarantee local invariance to time-shifting, which yields
\begin{equation}
\mathbf{S_2}\boldsymbol{x}(t,\gamma_1,\gamma_2) =
(\boldsymbol{x_2}(\cdot,\gamma_1,\gamma_2) \ast \phi)(t).
\end{equation}
